---
title: "R Notebook, Tarea 5"
subtitle: "Alejandro Poblete, Carlos Zavala"
output:
  html_document:
    df_print: paged
---


```{r setup, echo= FALSE}
library(tidyquant)
library(ggplot2)
```
#pregunta 2

se realiza la función que calcula retornos, graficos y jarque bera, se trabaja con precios adjusted

```{r acciones1, echo=TRUE}
AAPLE <- c("AAPL")
Microsoft <- c("MSFT")

MSFT <- tq_get(Microsoft, get="stock.prices",
               from="2000-01-01",
               to="2018-08-02",
               periodicity="monthly")

AAPL <- tq_get(AAPLE, get="stock.prices",
               from="2000-01-01",
               to="2018-08-02",
               periodicity="monthly")

```


```{r pregunta 2, echo=TRUE}

retorno2 <- function(x) {
  
  ret= exp(diff(log(x))) - 1
  ret2 <-data.frame(ret)
  
  g2 = ggplot(mapping=aes(ret))+ geom_histogram(aes(y=..density..),color='red',bins=50, alpha=0.5)+scale_fill_tq()+
    labs(title="Retornos")
  
  g22= ggplot(mapping = aes(x=x)) + geom_density(alpha=0.5)+ scale_fill_tq() + labs(title="Retornos densidad")
  
  acom= ggplot(ret2, aes(x=1:223, y=cumsum(ret))) + geom_line() + labs(title="Retornos acomulados") + ylab("retorno acomulado") + xlab("")
  
  ske = (1/length(x))*sum((x-mean(x))^3)/((1/length(x))*sum((x-mean(x))^2))^(3/2)
  kurt= (1/length(x))*sum((x-mean(x))^4)/((1/length(x))*sum((x-mean(x))^2))^(2)
  JB= length(x)*(((ske^2)/6)+ (((kurt-3)^2)/24))
  
  
  return (list(ret2, g2 ,print(paste("Jarque Bera", "=", JB, ",si JB > valor critico", ",Rechazo H0")),acom, g22))
}

```

```{r acciones, echo=TRUE}
retorno2(MSFT$adjusted)
retorno2(AAPL$adjusted)

```
#Pregunta 3


#Pregunta 3
#A

reps = 10000
betas = matrix(NA, nrow = reps, ncol = 8)
beta0 = 2
beta1 = 2.5
beta2 = 1
su = 1
v = beta2*X2 + u
n = c(50, 100, 500, 1000)                   #Tamaño muestral

for (j in 1:length(n)) {
  
  X1=rnorm(n[j],20,1)
  X2=0.8*X1 + e  
  
  for (i in 1:reps) {
    
    e = rnorm(n[i], 0, su)
    u = rnorm(n[i],0,su)
    X1= rnorm(n[i],20,1)
    
    Y = beta0 + beta1*X1 + v 
    
    model = lm(Y~X1 + X2)  
    
    betas[i,j] = model$coef[1]
    
    betas[i,j] = model$coef[2]
  }
}

betas_df <- data.frame(betas)
View(betas)

